---
title: "Presentation Linkedin data 4 competitive cities"
subtitle: "⚔<br/>with xaringan"
author: "Luisa M. Mimmi"
output:
  xaringan::moon_reader:
    css: ["default", "rladies", "rladies-fonts"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

class: inverse, center, middle



# OUTLINE

1. Conceptual Framework

1. Data exploration 

1. Further data exploration by city

1. Bivariate measures of association - categorical variables across cites

1. Zooming in on domestic migration

1. Relevant policy questions and potential follow-up

1. Reference
---

# Conceptual Framework

- A city's **productivity** can be simply defined as the net result of contrasting forces 
$$\ Productivity = Agglomeration (positive) - Congestion (negative)$$ 

- Both $\ Agglomeration$ and $\ Congestion$ could be modelled as a function of various dimensions $\ = f(Skills, Amenities, Form, Access)$
- Dimensions
    + **Skills**, a city’s aggregate stock of human capital
    + **Amenities** - _attracting 'skills'_ - job opportunities, housing values, cultural attractions
    + **Form**, the size and spatial configuration of a city (*density* vs. *sprawl*, *wider metropolitan areas*)
    + **Access**, a city’s connectedness (or barriers) to other cities, both at home and abroad, through the transportation network


.footnote[
[1] This comparative analysis will focus on the first dimension **Skills**, but keeping in mind also the other key dimensions that can explain the competitiveness of a city
]

---

# Data Exploration 

```{r global_options, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE, fig.align='center', echo=FALSE, eval=TRUE,warning=FALSE, message = FALSE)
```

```{r packages }
library(ggplot2) # install.packages("ggplot2")
library(dplyr)
library(knitr)
library(datasets) # initialize
library(kableExtra)
library(stats)
library(tidyr)
library(stringr)
library(stats)
```

```{r data }
# getwd()
migr <- read.csv("migration.csv",fileEncoding="UTF-8-BOM")
demog <- read.csv("demographics.csv",fileEncoding="UTF-8-BOM")
both <- left_join(demog,migr, by="NEW_MEM_ID")

```

## Metadata on the LinkedIn dataset

* Data contain *347 origin metro areas* and only *282 destinations*
* All Linkedin members (in data) have some tertiary education degree
* Linkedin members (in data) are distributed across *10 industry sectors* (plus 5 members with _unknown_ level)
  +  About 50% of them have an _Entry level_ job -> likely, active members are also people who look for jobs
* Linkedin members (in data) are distributed across *14 industry sectors* 
  + Highest % in _Government/Education/Non-profit_, followed by _Technology - Software_,  _Healthcare & Pharmaceutical_, and _Professional Services_
* Linkedin members (in data) are distributed across *26 job positions* 

---
#### Distribution of LinkedIn Members' _HIGHEST DEGREE_ across countries of origin - table
```{r}
#   Prop of members in each DEGREE to SUM of Country of origin
freq_OrigDegree <- both %>%
  group_by(both[,7],both[,2]) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  mutate(rel.freq = paste0(round(100 * n/sum(n), 2), "%"))
# freq_OrigDegree  # 

kable(freq_OrigDegree, format = "html") %>% kable_styling(bootstrap_options = c("striped", "hover", full_width = T , position = "center",font_size = NULL)) %>%
row_spec(5:8, color = "white", background = "#999999")
# %>%   group_rows("Australia", 1, 4) %>% group_rows("UK", 5, 8)  %>% group_rows("USA", 9, 12)
```
---
#### Distribution of LinkedIn Members' _HIGHEST DEGREE_ across countries of origin - Main findings

* The US has a significantly higher percentage of *_Associates_* migrants (18% vs 3% UK and 4% AUS)
    
    + **Question**: Is it due to a different education system in America? 
    
* Conversely, the proportions across country of _SENIORITY_ / _SECTOR_ / _POSITION_ appear remarkably similar across coountries
    
    + **Question**: Are this similarities due to a certain selection bias of the sample? Or, possibly mean that the three English speaking counties have homogenous job market and working populations?  
    

---
#### Top 10 _DESTINATION_ and _ORIGIN_ cities (mostly US)
```{r }
# create origin table
origin <- both %>% select(id=NEW_MEM_ID, degree=HIGHEST_DEGREE_OBTAINED, seniority=SENIORITY, sector=EMPLOYER_INDUSTRY_SECTOR, role=POSITION_FUNCTION, date=WEEK_BEGINNING, countryO=SOURCE_COUNTRY, cityO=SOURCE_REGION)

# create destination table
destination <- both %>% select(id=NEW_MEM_ID, degree=HIGHEST_DEGREE_OBTAINED, seniority=SENIORITY, sector=EMPLOYER_INDUSTRY_SECTOR, role=POSITION_FUNCTION, date=WEEK_BEGINNING, countryD=DESTINATION_COUNTRY, cityD=DESTINATION_REGION)

# Aggregate N flow (OUT) by City
aggreOrig <- origin  %>% 
  group_by(cityO) %>% 
  summarize(NumOutflow= n())  %>% 
  mutate(freq = NumOutflow / sum(NumOutflow)) %>%
  mutate(rel.freq = as.numeric(paste0(round(100 * NumOutflow/sum(NumOutflow), 3))))  %>% 
  arrange(desc(NumOutflow))

# Aggregate N flow (IN) by City
aggreDest <- destination  %>% 
  group_by(cityD) %>% 
  summarize(NumInflow= n())  %>% 
  mutate(freq = NumInflow / sum(NumInflow)) %>%
  mutate(rel.freq = as.numeric(paste0(round(100 * NumInflow/sum(NumInflow), 3))))  %>% 
  arrange(desc(NumInflow))

aggreByCity <- full_join(aggreDest,aggreOrig, by = c("cityD" = "cityO")) 
aggreByCity[c("NumInflow", "NumOutflow")][is.na(aggreByCity[c("NumInflow", "NumOutflow")])] <- 0

aggreByCity <-  aggreByCity %>% 
  select(-freq.x,-rel.freq.x, -freq.y, -rel.freq.y) %>%  # get rid of meeaningless 
  mutate (NetFlow= NumInflow -NumOutflow) %>% # Net 
  mutate (NegOutFlow= -(NumOutflow)) %>% # neg sign 
  mutate (Sign = ifelse(NetFlow > 0, "Positive", "Negative")) %>%
  mutate (colour= ifelse(NetFlow > 0, "positive", "negative")) %>%  mutate (city_copy = cityD)  %>%  
  separate(city_copy, into = c("city_only", "metro area"), sep = ",")

# ====================== INTERIM ======================= #
names(aggreByCity)[1]<-"city"
names(migr)[4]<-"city"
# city_country <-full_join(aggreByCity, migr, by = c("city", "SOURCE_REGION")) %>%  # #select(city,country=origCountry)

city_country <-full_join(aggreByCity, migr, by = "city") %>%  
  select(city, country=DESTINATION_COUNTRY) %>%
  distinct () %>% # need the dup flag 
  mutate(dupli = ifelse((city =="Greater New York City Area"|city =="San Francisco Bay Area" |city =="Washington D.C. Metro Area"|
  city =="Greater Los Angeles Area"|city =="Greater Boston Area"|city =="Greater Chicago Area" |
  city =="Dallas/Fort Worth Area" |city =="Greater Seattle Area" |city =="San Francisco Bay Area") & country!="United States", "dup", "")) %>% # need the dup flag 
    mutate(dupli2 = ifelse((city =="London, United Kingdom") & country!="United kindom", "dup", "")) %>% # need the dup flag 
    mutate(dupli3 = ifelse((city =="Sydney Area, Australia") & country!="Australia", "dup", "")) %>% # need the dup flag 
    mutate(dupli4 = ifelse((city =="Perth Area, Australia") & country!="Australia", "dup", "")) %>% # need the dup flag 
    mutate(dupli5 = ifelse((city =="Miami/Fort Lauderdale Area") & country!="United States", "dup", "")) %>% # need the dup flag 
    mutate(dupli6 = ifelse((city =="Brisbane Area, Australia") & country!="Australia", "dup", "")) 

city_country <- subset(city_country, city_country$dupli!="dup" & city_country$dupli2!="dup" & city_country$dupli3!="dup" & city_country$dupli4!="dup" & city_country$dupli5!="dup" & city_country$dupli6!="dup") %>% select(city, country)

newRow <- data.frame(city ="London, United Kingdom", country ="United Kingdom" )

city_country <- rbind(city_country,newRow)
#city_country <- rbind(city_country, c("London, United Kingdom", "United kindom"))
  
names(aggreByCity)[1]<-"cityD"
```


```{r ,include=FALSE, fig.width=10, fig.height=7}
names(aggreByCity)[1]<-"city"

# 1) In  Flow in Top DESTINATION 
Top_in <- aggreByCity %>% top_n(10, NumInflow)  
  Top_in$city = with(Top_in, reorder(city,NumInflow)) # reorder Levels by Var

Top_in <- ggplot(data = Top_in,aes(city, NumInflow)) + 
  geom_bar(stat = "identity", position="identity", fill = "steelblue") +
  geom_hline(yintercept=10000, color = "black", size=0.5) +
  theme(axis.text.x = element_text(angle=60, vjust=0.3), axis.text.y = element_text(size=10,face="bold") ) + 
  labs(title="IN flow in top 10 destination", x="")

Top_in + coord_flip()

```


```{r , include=FALSE, fig.width=10, fig.height=7}
# 2) Out  Flow in Top ORIGIN 
Top_out <- aggreByCity %>% top_n(15, NumOutflow)  
  Top_out$city = with(Top_out, reorder(city,NumOutflow)) # reorder Levels by Var

Top_out <- ggplot(data = Top_out,aes(city, NegOutFlow)) + 
  geom_bar(stat = "identity", position="identity", fill = "firebrick1") + 
   geom_hline(yintercept=-10000, color = "black", size=0.5) +
  theme(axis.text.x = element_text(angle=60, vjust=0.3), axis.text.y = element_text(size=10,face="bold") ) + 
  labs(title="OUT flow in top 10 origin", x="") 
  
Top_out + coord_flip()
```


```{r ,fig.width=10, fig.height=5}
in_flip<- Top_in + coord_flip()
out_flip <- Top_out + coord_flip()

# plot side by side 
 library(gridExtra)
 grid.arrange(in_flip, out_flip, ncol=2)
```
* Understandably, these are mostly American cities, although London is # 5 Destination and # 10 Origin for migrants
* Interestingly, 9/10 of top _destinations_ are the same as top _origin_ cities
    + There may be high inter-city *mobility*, but not necessarily other dimensions (*Amenities*, *Access*) of competitiveness, such that people decide to stay
    + Or, it may just be the American way of moving to and from college!

---

#### What about the *NET  * migration flow to & from Top 20 cities? 
```{r ,fig.width=8, fig.height=5}
# 3.a)  NET flow in Top  DESTINATION 
Top_net <- aggreByCity %>% top_n(20, NumInflow)  
  Top_net$city = with(Top_net, reorder(city,NumInflow)) # reorder Levels by Var

Top_net <- ggplot(data = Top_net,aes(city, NetFlow)) + 
  geom_bar(stat = "identity", position="identity",aes(fill = colour)) + 
  theme(axis.text.x = element_text(angle=60, vjust=0.3), axis.text.y = element_text(size=10,face="bold") ) + 
  scale_fill_manual(values=c(positive="steelblue",negative="firebrick1")) +
  labs(title="NET migration flow in first 20 destination", subtitle="(ordered by destination)", x="")

Top_net + coord_flip()
```

* Overall, most of the top American destination cities maintain a strong positive net flow of migrants. 
* Chicago, Philadelphia and Miami had a negative net flow over 2016
  + Given Miami's position as a main entry port for Latin American migrants, this is a bit hard to believe. Possibly suggests non-representativity of Linkedin dataset for capturing the whole migrant population

---

#### Top 20 DESTINATION cities for migrants in UK 
```{r interim UK  }
# add country to aggreByCity
aggreByCity2 <- left_join(aggreByCity,city_country,by = "city")

# x[c("a", "b")][is.na(x[c("a", "b")])] <- 0
aggreByCity2[c("NumInflow", "NumOutflow")][is.na(aggreByCity2[c("NumInflow", "NumOutflow")])] <- 0

```

```{r top UK ,fig.width=8, fig.height=5 }
aggreByCityUK <- aggreByCity2 %>% 
  filter (country == "United Kingdom")
 
Top_inUK <- aggreByCityUK %>% 
  top_n(20, NumInflow)  

Top_inUK$city = with(Top_inUK, reorder(city,NumInflow)) # reorder Levels by Var

Top_inUK <- ggplot(data = Top_inUK,aes(city, NumInflow)) + 
  geom_bar(stat = "identity", position="identity", fill = "steelblue") +
  geom_hline(yintercept=10000, color = "black", size=0.5) +
  theme(axis.text.x = element_text(angle=60, vjust=0.3), axis.text.y = element_text(size=10,face="bold") ) + 
  labs(title="IN migration flow in first 20 destination")


Top_inUK + coord_flip()


```
* Contrary to the USA's generalized high mobility across the whole country, in the UK, London is definitively an outlier
* This makes sense in light of London special role as European *hub*, at least for financial and other sectors 

---

#### Top 20 ORIGIN cities for migrants in UK 

```{r,fig.width=8, fig.height=5}
# 2) Out  Flow in Top ORIGIN 
Top_outUK <- aggreByCityUK %>% 
  filter (country == "United Kingdom") %>% # filter by country = UK 
  top_n(20, NumOutflow)  
  Top_outUK$city = with(Top_outUK, reorder(city,NumOutflow)) # reorder Levels by Var

Top_outUK <- ggplot(data = Top_outUK,aes(city, NegOutFlow)) + 
  geom_bar(stat = "identity", position="identity", fill = "firebrick1") + 
   geom_hline(yintercept=-10000, color = "black", size=0.5) +
  theme(axis.text.x = element_text(angle=60, vjust=0.3), axis.text.y = element_text(size=10,face="bold") ) + 
  labs(title="OUT migration flow in first 20 origin") 
  
Top_outUK + coord_flip()
```

* Yet, similar to the top US destination cities, London is also a place from which many people leave  
---

#### Net migrants flows in top 20 ORIGIN cities in UK 

```{r,fig.width=8, fig.height=5}
# 3.a)  NET flow in Top  DESTINATION 
Top_netUK <- aggreByCityUK %>% 
   filter (country == "United Kingdom") %>% # filter by country = UK 
  top_n(20, NumInflow)  
  Top_netUK$city = with(Top_netUK, reorder(city,NumInflow)) # reorder Levels by Var

Top_netUK <- ggplot(data = Top_netUK,aes(city, NetFlow)) + 
  geom_bar(stat = "identity", position="identity",aes(fill = colour)) + 
  theme(axis.text.x = element_text(angle=60, vjust=0.3), axis.text.y = element_text(size=10,face="bold") ) + 
  scale_fill_manual(values=c(positive="steelblue",negative="firebrick1")) +
  labs(title="NET migration flow in first 20 destination", subtitle="(ordered by destination)")
Top_netUK + coord_flip()
```
* In 2016, London had a net positive flow of migrants (followed at a distance by Manchester), while the other British cities where mostly loosing citizens
  
---

#### Top 20 DESTINATION cities for migrants in AUSTRALIA 
```{r interim AUSTRALIA  }
aggreByCityAustr <- aggreByCity2 %>% 
  filter (country == "Australia")
```

```{r top AUSTRALIA ,fig.width=8, fig.height=5 }

Top_inAustr <- aggreByCityAustr %>% 
  top_n(20, NumInflow)  

Top_inAustr$city = with(Top_inAustr, reorder(city,NumInflow)) # reorder Levels by Var

Top_inAustr <- ggplot(data = Top_inAustr,aes(city, NumInflow)) + 
  geom_bar(stat = "identity", position="identity", fill = "steelblue") +
  geom_hline(yintercept=3000, color = "black", size=0.5) +
  theme(axis.text.x = element_text(angle=60, vjust=0.3), axis.text.y = element_text(size=10,face="bold") ) + 
  labs(title="IN migration flow in top 20 destination")


Top_inAustr + coord_flip()

```

* Evidently the magnitude of migration flows is much smaller in Australia
  + While I don't have the population sizes for comparison, it would seem Australian LinkedIn members move less than their counter-parts
---

#### Top 20 ORIGIN cities for migrants in AUSTRALIA 

```{r,fig.width=8, fig.height=5}
# 2) Out  Flow in Top ORIGIN 
Top_outAustr <- aggreByCityAustr %>% 
  filter (country == "Australia") %>% # filter by country = Austr 
  top_n(20, NumOutflow)  
  Top_outAustr$city = with(Top_outAustr, reorder(city,NumOutflow)) # reorder Levels by Var

Top_outAustr <- ggplot(data = Top_outAustr,aes(city, NegOutFlow)) + 
  geom_bar(stat = "identity", position="identity", fill = "firebrick1") + 
   geom_hline(yintercept=-3000, color = "black", size=0.5) +
  theme(axis.text.x = element_text(angle=60, vjust=0.3), axis.text.y = element_text(size=10,face="bold") ) + 
  labs(title="OUT migration flow in top 20 origin") 
  
Top_outAustr + coord_flip()
```
* In 2016, migrants were also leaving from most cities in great numbers
---

#### Net migration flows in top 20 ORIGIN cities in AUSTRALIA 

```{r,fig.width=8, fig.height=5}
# 3.a)  NET flow in Top  DESTINATION 
Top_netAustr <- aggreByCityAustr %>% 
   filter (country == "Australia") %>% # filter by country = Austr 
  top_n(20, NumInflow)  
  Top_netAustr$city = with(Top_netAustr, reorder(city,NumInflow)) # reorder Levels by Var

Top_netAustr <- ggplot(data = Top_netAustr,aes(city, NetFlow)) + 
  geom_bar(stat = "identity", position="identity",aes(fill = colour)) + 
  theme(axis.text.x = element_text(angle=60, vjust=0.3), axis.text.y = element_text(size=10,face="bold") ) + 
  scale_fill_manual(values=c(positive="steelblue",negative="firebrick1")) +
  labs(title="NET migration flow in top 20 destination", subtitle="(ordered by destination)")
Top_netAustr + coord_flip()
```
* The net flow figures, depicts a much more mixed situation than the UK. 
  + 2 other cities (beyond the capital), Brisbane and Canberra, have been quite attractive in 2016
  + Conversely, several cities (notably Perth and Adelaide) have lost a lot of workers in 2016 


---
# Further data exploration by city
### Bivariate measures of association 

Upon studying the migration patterns in general, I now want to check if there is any relation between destination/origin of migration and the other variables in the dataset. 

As an example, I select the top 3 cities of destination in the 3 countries:  

* Greater New York City Area
* San Francisco Bay Area
* Washington D.C. Metro Area
* Manchester, United Kingdom
* London, United Kingdom
* Birmingham, United Kingdom
* Sydney Area, Australia
* Brisbane Area, Australia
* Canberra Area, Australia

```{r}
top_dest <- c("Greater New York City Area" , "San Francisco Bay Area",  "Washington D.C. Metro Area" , "Manchester, United Kingdom", "London, United Kingdom" ,"Birmingham, United Kingdom" ,"Sydney Area, Australia","Brisbane Area, Australia" ,"Canberra Area, Australia")

 # both_top <- both[as.character(  both$DESTINATION_REGION %in% top_dest), drop = T]

# data[data$Code %in% selected,]
# both_top <- both[both$DESTINATION_REGION %in% top_dest]
# both_top <- both[as.character(  both$DESTINATION_REGION %in% top_dest), drop = TRUE]

# 4) attemps
# data[data$Code == "A" | data$Code == "B", ]
top3cit <- both[both$DESTINATION_REGION == "Greater New York City Area" | both$DESTINATION_REGION == "San Francisco Bay Area"  | both$DESTINATION_REGION == "Washington D.C. Metro Area" | both$DESTINATION_REGION == "Manchester" | both$DESTINATION_REGION == "United Kingdom"| both$DESTINATION_REGION == "London, United Kingdom" | both$DESTINATION_REGION =="Birmingham, United Kingdom" | both$DESTINATION_REGION =="Sydney Area, Australia"| both$DESTINATION_REGION =="Brisbane Area, Australia" | both$DESTINATION_REGION =="Canberra Area, Australia" ,  ]


# 5) attemps
# top_dest <- c("Greater New York City Area" , "San Francisco Bay Area",  "Washington D.C. Metro Area" , "Manchester, United Kingdom", "London, United Kingdom" 
```

---
#### Distribution of HIGHEST DEGREE obtained across top 3 destination cities in 3 countries 
```{r , include=FALSE}
# grafici senza farli 
# qplot
degree_q<- qplot(x = DESTINATION_REGION, data = top3cit, fill = HIGHEST_DEGREE_OBTAINED, geom = "bar") +
theme(axis.text.x = element_text(angle=75, vjust=0.3), axis.text.y = element_text(size=10,face="bold") )  +  
  labs(title="Highest degree across top 3 city in 3 countries" , x="", y="N. of people coming IN")
# ggplot

#ggplot(data = Best_out,aes(cityD, NegOutFlow)) + 
#  geom_bar(stat = "identity", position="identity", fill = "firebrick1") + 
#   geom_hline(yintercept=-10000, color = "black", size=0.5) +
#  theme(axis.text.x = element_text(angle=60, vjust=0.3)) + 
#  labs(title="OUT migration flow in first 15 destination") 


degree_g <- ggplot(top3cit, aes(x=DESTINATION_REGION, y=NEW_MEM_ID, fill=HIGHEST_DEGREE_OBTAINED)) +  
  geom_bar(aes(colour =HIGHEST_DEGREE_OBTAINED),stat="identity", position = "fill") +
  theme(axis.text.x = element_text(angle=75, vjust=0.3), axis.text.y = element_text(size=10,face="bold") )  +
  labs(title="Highest degree across top 3 city in 3 countries" , x="", y="N. of people coming IN normalized") 
```




```{r ,fig.width=10, fig.height=6}
# in_flip<- Top_in + coord_flip()
# out_flip <- Top_out + coord_flip()

# plot side by side 
 library(gridExtra)
 grid.arrange(degree_q, degree_g, ncol=2)
```

* San Francisco (followed by Canberra) seems to attract the highest amount of doctors: With Canberra receiving also the highest group of master holders 
* NY, San Francisco and Washington DC seem to receive many with "Associate" level: possibly young people looking for their first job
 
---
#### SECTOR distribution across top 3 destination cities in 3 countries 
```{r , include=FALSE}
# grafici senza farli 
# qplot
sector_q <-    qplot(x = DESTINATION_REGION, data = top3cit, fill = EMPLOYER_INDUSTRY_SECTOR, geom = "bar") +
theme(axis.text.x = element_text(angle=75, vjust=0.3), axis.text.y = element_text(size=10,face="bold") )  +
 labs(title="SECTOR across top 3 city in 3 countries", x="", y="Number of people coming IN")

# ggplot
library(RColorBrewer)
display.brewer.all()

sector_g <-  ggplot(top3cit, aes(x=DESTINATION_REGION, y=NEW_MEM_ID, fill=EMPLOYER_INDUSTRY_SECTOR)) +  
  geom_bar(aes(colour =EMPLOYER_INDUSTRY_SECTOR),stat="identity",  position = "fill") +
theme(legend.position = "right"    ,axis.text.x = element_text(angle=75, vjust=0.3), axis.text.y = element_text(size=10,face="bold") )  +
   # scale_fill_brewer(palette = "Dark2") +
  # scale_fill_grey() +
  labs(title="SECTOR across top 3 city in 3 countries", x="", y="Number of people coming IN normalized")
```




```{r ,fig.width=10, fig.height=6}
# in_flip<- Top_in + coord_flip()
# out_flip <- Top_out + coord_flip()

# plot side by side 
 library(gridExtra)
 grid.arrange(sector_q, sector_g, ncol=2)
```

---

#### Interesting correlation between the two variables *SECTOR* & *city of destination* 


* Not surprisingly, the share of immigrants by sector seems to vary a lot in a way that is correlated to the city of destination
   + Extremely high number in Govv/ Educ/ Non Profit in _Canberra_ & _Washington_
   + Extremely high number in Software + Hardware Technology in _San Francisco_
   + Extremely high number in Govv/ Educ/ Non Profit + Financial Services also in _NY_


* This intuitive fact (especially knowing how American cities's sector specialization), is also validated by calculating `Cramer's V`
    + (Pearson chi-square statistic rescaled to have values between [0-1])

$$\ V = \sqrt \frac{X^2}{[nobs * (min(ncols, nrows) – 1)]}$$

* The Cramer’s V statistic has the highest value for _Sector_ and _Destination Region_ = 0.1605205
---

# Zooming in on domestic migration
```{r include=FALSE}
# select only USA
both_USA <- both %>% filter(SOURCE_COUNTRY=="United States" & DESTINATION_COUNTRY=="United States")
# select only Australia
both_AUS <- both %>% filter(SOURCE_COUNTRY=="Australia" & DESTINATION_COUNTRY=="Australia")
# select only UK
both_UK <- both %>% filter(SOURCE_COUNTRY=="United Kingdom" & DESTINATION_COUNTRY=="United Kingdom")

# iinternal sub-sample (for simplicity)
both_USA_N <- both_USA %>% group_by(DESTINATION_REGION) %>%  summarise(numIMM = n())
both_USA_N

some_USA <- both_USA[both_USA$DESTINATION_REGION == "Greater New York City Area" | both_USA$DESTINATION_REGION == "San Francisco Bay Area"  | both_USA$DESTINATION_REGION == "Washington D.C. Metro Area" | both_USA$DESTINATION_REGION == "Greater Los Angeles Area" | both_USA$DESTINATION_REGION == "Greater Boston Area"| both_USA$DESTINATION_REGION == "Greater Seattle Area" | both_USA$DESTINATION_REGION =="Austin, Texas Area" | both_USA$DESTINATION_REGION =="Miami/Fort Lauderdale Area"| both_USA$DESTINATION_REGION =="Hawaiian Islands" | both_USA$DESTINATION_REGION =="Savannah, Georgia Area" 
                    | both_USA$DESTINATION_REGION == "Green Bay, Wisconsin Area" | both_USA$DESTINATION_REGION =="St. Cloud, Minnesota Area" | both_USA$DESTINATION_REGION =="Greenville, North Carolina Area"| both_USA$DESTINATION_REGION =="Houston, Texas Area" | both_USA$DESTINATION_REGION =="Savannah, Georgia Area" 
                    ,  ]

summary(some_USA)

# some UK 
both_UK_N <- both_UK %>% group_by(DESTINATION_REGION) %>%  summarise(numIMM = n())
both_UK_N

some_UK <- both_UK[both_UK$DESTINATION_REGION == "London, United Kingdom" | both_UK$DESTINATION_REGION == "Edinburgh, United Kingdom"  | both_UK$DESTINATION_REGION == "Cambridge, United Kingdom" | both_UK$DESTINATION_REGION == "Oxford, United Kingdom" | both_UK$DESTINATION_REGION == "Glasgow, United Kingdom"| both_UK$DESTINATION_REGION == "Twickenham, United Kingdom" | both_UK$DESTINATION_REGION =="Coventry, United Kingdom" | both_UK$DESTINATION_REGION =="Harrow, United Kingdom"| both_UK$DESTINATION_REGION =="Cardiff, United Kingdom" | both_UK$DESTINATION_REGION =="Hemel Hempstead, United Kingdom" 
                    | both_UK$DESTINATION_REGION == "Bromley, United Kingdom" | both_UK$DESTINATION_REGION =="Stockport, United Kingdom" | both_UK$DESTINATION_REGION =="Chelmsford, United Kingdom"| both_UK$DESTINATION_REGION =="Stevenage, United Kingdom" | both_UK$DESTINATION_REGION =="Belfast, United Kingdom" 
                    ,  ]

summary(some_UK)

```



It would be interesting to see how this noticeable association (between sector and destination city) plays out when looking at domestic migration only.

Here are the findings per country:

1. USA:        `Cramer's V` =  0.1270301 
2. Australia:  `Cramer's V` =  0.1074171
3. UK:         `Cramer's V` =    0.07060599

In the next 3 slides, the same association is illustrated graphically

.footnote[
[1] For plotting simplicity, I used random sub-samples of cities for US and UK

]

---

#### Correlation between *sector* & *city of destination* - USA domestic migration 
```{r ,fig.width=7, fig.height=7}
# ggplot
ggplot(some_USA, aes(x=DESTINATION_REGION, y=NEW_MEM_ID, fill=EMPLOYER_INDUSTRY_SECTOR)) +  
  geom_bar(aes(colour =EMPLOYER_INDUSTRY_SECTOR),stat="identity",  position = "fill") +
theme(legend.position = "right"    ,axis.text.x = element_text(angle=75, vjust=0.3), axis.text.y = element_text(size=10,face="bold") )  +
  
   # scale_fill_brewer(palette = "Dark2") +
  # scale_fill_grey() +
  labs(title="SECTOR across various US cities", x="", y="Number of people coming in normalized")

```
---

#### Correlation between *sector* & *city of destination* - AUS domestic migration 

```{r ,fig.width=7, fig.height=7}

# ggplot
ggplot(both_AUS, aes(x=DESTINATION_REGION, y=NEW_MEM_ID, fill=EMPLOYER_INDUSTRY_SECTOR)) +  
  geom_bar(aes(colour =EMPLOYER_INDUSTRY_SECTOR),stat="identity",  position = "fill") +
theme(legend.position = "right"    ,axis.text.x = element_text(angle=75, vjust=0.3), axis.text.y = element_text(size=10,face="bold") )  +
  
   # scale_fill_brewer(palette = "Dark2") +
  # scale_fill_grey() +
  labs(title="SECTOR across AUS cities", x="", y="Number of people coming in normalized")


```
---

#### Correlation between *sector* & *city of destination* - UK domestic migration 
```{r ,fig.width=7, fig.height=7}


# ggplot
ggplot(some_UK, aes(x=DESTINATION_REGION, y=NEW_MEM_ID, fill=EMPLOYER_INDUSTRY_SECTOR)) +  
  geom_bar(aes(colour =EMPLOYER_INDUSTRY_SECTOR),stat="identity",  position = "fill") +
theme(legend.position = "right"    ,axis.text.x = element_text(angle=75, vjust=0.3), axis.text.y = element_text(size=10,face="bold") )  +
  
   # scale_fill_brewer(palette = "Dark2") +
  # scale_fill_grey() +
  labs(title="SECTOR across some UK cities", x="", y="Number of people coming in normalized")

```


---
# Relevant policy questions and potential follow-up

The data - describing certain characteristics of 2016 migrants from 3 countries - is limited to 1 year and there is likely some selection bias that challenges the representativity of this sample. The sample could be biased towards highly educated, (obviously) internet-savvy, and likely skewed towards a young-ish stratum of the actual working/migrant population.

Nonetheless, the analysis of this dataset offered some very interesting insights. Some of the findings are not surprising, but some raise some crucial questions that policymakers should carefully consider if they intend to foster the competitiveness of cities. 

To answer some of these questions, it would be extremely interesting to combine the Linkedin data with data from other sources that can make the information more complete and relevant. 

---

### Follow-up question # 1 and relevant external data sources

The most attractive cities have also lost many people over the past year. It would be advisable to combine the information about in-demand sectors and position with other **Amenities** that determine people's choices to relocate. It is plausible that _rent_ in NY, DC or San Francisco is a strong deterrent, particularly for workers in "noncutting-edge" sectors if their _salary_ is not growing at the same rate. 

DATA SOURCE: [glassdoor](https://www.glassdoor.com/Salaries/index.htm) could be an interesting source because it has granular and comparable data on salaries that can be analyzed by _SECTOR_, _POSITION_, _CITY_

---

### Follow-up question # 2 and relevant external data sources
Another important aspect for promoting cities' competitiveness is that they are actually not isolated entities, but rather _systems of cities_ in that a healthy level of mobility can foster the exchange of **Skills** (intended as the individual city's collective human capital). 

Clearly, the US shows a much higher and much more widespread mobility - at least in major towns all over the states. It could seem odd that in seemingly smaller countries the all mobility affect 2/3 top cities. My guess is that infrastructure and cultural factors are jointly at play.  

Not so long ago, the World Bank hosted a very stimulating conference on "Space and Productivity" and will soon hold its "2nd Geospatial Day": just a couple of examples of how crucial it is to design place-based policies that acknowledge the fundamental importance of the **Form** and **Access** explanatory dimensions of the city/cities productivity function. 

DATA SOURCES: the [Space & Productivity](http://www.worldbank.org/en/events/2017/09/28/space-and-productivity-conference) conference and  [Geospatial Blog](https://blogs.worldbank.org/category/tags/geospatial-technology) are good places to start.
---


class: center, middle

# Thank You!


---

# Reference

* The conceptual framework is borrowed from a very interesting forthcoming report by some colleagues at the World Bank: 
   + Ferreyra M.M, Roberts M. Lozano Gracia N. Restrepo Cadavid M., Selod H,. 2017 (forthcoming). _Falling Short - Cities and Productivity in Latin America and the Caribbean_. World Bank Group. Washington D.C.

* The slides were created via the R package  [**xaringan**](https://github.com/yihui/xaringan) created by '*Presentation Ninja*' Yihui Xie


